MS&E 226: Project Part 1 Code

### 2024-12-03 MS&E 226_Project Part 2_Code.Rmd
2e multiple hypothesis testing

@@

>>>>

#### (d)

@@

#### (e)

```{r Benjamini_Hochberg Procedure}

# Extract the p-values for the coefficients
p_values <- summary(ols_test)$coefficients[, 4] # 4th column contains p-values

# Apply the Benjamini-Hochberg procedure
adjusted_p_values <- p.adjust(p_values, method = "BH")

# Combine the results into a summary dataframe
results <- data.frame(
  Coefficient = rownames(summary(ols_test)$coefficients),
  P_Value = p_values,
  Adjusted_P_Value = adjusted_p_values
)

# Display the results
print(results)

# Optional: Identify which hypotheses are significant after FDR correction
significant <- results$Adjusted_P_Value < 0.05
results$Significant <- ifelse(significant, "Yes", "No")

# Display the results with significance labels
print(results)

#### GRAVEYARD
